Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-07 Manuscript for submission/manuscript.tex
Update

%Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
For the convenience of theoretical investigation, we slightly modify the first term in the objective function summing over all $(i,j)$ pairs.
After scaling, due to symmetry of $X$,$L$, and $S$, the only difference between (\ref{eq:logistic10}) and (\ref{eq:Modified}) is in the inclusion of terms in diagonal pairs $(i,i),\forall i=1,\dots,n$.
%the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
Let $\widehat{\Theta}$ and $\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \widehat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
\widehat{\Delta}^{\alpha} = \widehat{\alpha}-\alpha^{*},
\widehat{\Delta}^L = \widehat{L}-L^{*},
\widehat{\Delta}^S = \widehat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
We then impose several assumptions for theoretical guarantees of our estimator.

@@

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$. We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}. We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
\end{assumption}

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
    :=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align} \label{theorem1}
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
whereas Agarwal, et al.\cite{agarwal2012noisy} work on a general linear observation model whose parameter is also 
characterized by sum of a low rank matrix and a sparse matrix.

@@

Astute readers might have noticed that the upper bound in \ref{theorem1} consists of three different terms, where we denote them as
$\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$. 
Each respective term is involved with estimating three model parameters, $\alpha, L$ and $S$.
To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
1) The first one is called as an ``estimation error''. 
This error represents the statistical cost of estimating parameters which belong to the model subspace. 
2) Another quantity is referred as ``approximation error''. 
This error occurs when we only focus on estimating parameters within the model subspace, 
and it shrinks as the model subspace becomes large.
%=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}

@@

\subsection{Numerical experiments with synthetic data}
\label{sec:Syn-dat}
First, we introduce two synthetic scenarios that we want to explore.
Then, we describe three model selection criteria and four evaluation metrics for the selected model.
Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results.

\subsubsection{Synthetic Setting}
%In this subsection, we consider the following $3$ scenarios:
%In this subsection, we consider $3$ scenarios.
%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
%In third scenario, we consider a situation
Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.

@@

    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           &\vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\subsubsection{Choosing the tuning parameters and evaluation criteria}
Choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $15$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
An index of the point, which is to the left of this elbow point, is considered as the number of the topics embedded in the network.
(We will denote this number as $\widehat{K}^{\text{Scree}}$.)
We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}}$
and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
Once we find a grid, which satisfies above constraints, we choose a pair of tuning parameters: %($\gamma^{\text{Heu}},\delta^{\text{Heu}}$):
\[
    (\gamma^{\text{Heu}},\delta^{\text{Heu}}):=
    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}
\]
One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \bigg(\frac{n(n-1)}{2}\bigg),
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|.
\]
Here $M$ indicates the current model, which is implicitly understood that the model is obtained from certain tuning parameter pair $(\gamma,\delta)$.
We use $\mathbb{L}_n( \hat{\beta}(M))$ to denote the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $\widehat{S}^{\gamma,\delta}$ and the low-rank matrix $\widehat{L}^{\gamma,\delta}$.
In detail, if we have $\text{rank}(\widehat{L}^{\gamma,\delta})=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} \neq 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
\]
since the number of free parameters in $\widehat{L}^{\gamma,\delta}$ is $K$ plus $nK - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
Additional $1$ in the last term is due to $\hat{\alpha}$.
We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) and AIC($M$) as a function of $(\gamma,\delta)$ respectively, where we denote them as follows:
\[
    (\gamma^{BIC},\delta^{BIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{BIC}(M),
    \quad
    (\gamma^{AIC},\delta^{AIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{AIC}(M)
\]
We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics.

@@

\subsubsection{Several Observations}
%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
%Furthermore, we find one interesting phenomenon.
%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
\begin{enumerate}
    \item \textbf{Model Selection.}
    First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
    As presented in Table.\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings. This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios. (See Fig.\ref{fig:figure2})

    \begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &    1 (3)  &    0 (2)   &  0 (2)  &    1 (4)    &  0 (3)   &  0 (3)  &    1 (5)  &   0 (4)    & 0 (4) \\
    $M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
    $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
    $M_{4}$   &  0  &   $\frac{10}{30}$    &  $\frac{10}{30}$    &   0          &   $\frac{20}{80}$    &   $\frac{20}{80}$   &  0      &  $\frac{24}{120}$     &   $\frac{24}{120}$   \\
                \hline
    \end{tabular}

>>>>

%Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
For the convenience of theoretical investigation, we slightly modify the first term in the objective function summing over all $(i,j)$ pairs.
After scaling, due to symmetry of $X$,$L$, and $S$, the only difference between (\ref{eq:logistic10}) and (\ref{eq:Modified}) is in the inclusion of terms in diagonal pairs $(i,i),\forall i=1,\dots,n$.
%the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
Let $\widehat{\Theta}$ and $\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \widehat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
\widehat{\Delta}^{\alpha} = \widehat{\alpha}-\alpha^{*},
\widehat{\Delta}^L = \widehat{L}-L^{*},
\widehat{\Delta}^S = \widehat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\bigg\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\bigg\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
We then impose several assumptions for theoretical guarantees of our estimator.

@@

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L}) \label{Ass:2}
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume that the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, where $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$.
\end{assumption}

\begin{assumption} (\textbf{Spikiness of L and Constraint on $\alpha$}) \label{Ass:3}
We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}. We would also like to note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
\end{assumption}

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)
    :=\big\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\big\|_{F}^{2} + \big\|\widehat{\Delta}^{L}\big\|_{F}^{2} + \big\|\widehat{\Delta}^{S}\big\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1}, \ref{Ass:2} and \ref{Ass:3},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big)$
\begin{align} \label{theorem1}
    e^{2}\big(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}\big) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most $s$.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
whereas Agarwal, et al. \cite{agarwal2012noisy} work on a general linear observation model whose parameter is also
characterized by sum of a low rank matrix and a sparse matrix.

@@

Astute readers might have noticed that the upper bound in \eqref{theorem1} consists of three different terms, where we denote them as
$\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$.
Each respective term is involved with estimating three model parameters, $\alpha, L$ and $S$.
To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
1) The first one is called as an ``estimation error.''
This error represents the statistical cost of estimating parameters that belong to the model subspace.
2) Another quantity is referred as ``approximation error.''
This error occurs when we only focus on estimating parameters within the model subspace,
and it shrinks as the model subspace becomes large.
%=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}

@@

\subsection{Numerical experiments with synthetic data}
\label{sec:Syn-dat}
First, we introduce two synthetic scenarios that we want to explore (Section \ref{sec:Syn-set}).
Then, we describe three model selection criteria and four evaluation metrics for the selected model
(Section \ref{sec:Eval-crit}).
Subsequently, we elaborate experimental results from the synthetic networks and several interesting findings from those results (Section \ref{sec:obs}).

\subsubsection{Synthetic Setting} \label{sec:Syn-set}
%In this subsection, we consider the following $3$ scenarios:
%In this subsection, we consider $3$ scenarios.
%In first scenario, we examine a simple setting, in which every paper in the network has only one topic.
%In second scenario, we study a more complicated situation than the first one where each paper in the network can possibly have more than one topic.
%It is worth noting that different clusters of papers, where each cluster is comprised of papers with same topic, are connected via ad-hoc links.
%In third scenario, we consider a situation
Before specifying the network settings in two scenarios that we want to explore, let us first describe a set of procedures for setting the model parameters, $\alpha^*, F^*, D^*$ and $S^*$ sequentially.

@@

    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           & \quad \vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\subsubsection{Choosing the tuning parameters and evaluation criteria} \label{sec:Eval-crit}
Choosing a good pair of tuning parameters is an important yet challenging issue in our setting.
Here we present a heuristic procedure for choosing a good pair of tuning parameters $(\gamma,\delta)$.
Following the scree-plot approach in Ji and Jin \cite{ji2016coauthorship}, we plot the largest $15$ eigenvalues of the adjacency matrix $X$, and find an ``elbow'' point where the eigenvalues seem to level off.
An index of the point, which is to the left of this elbow point, is considered as the number of the topics embedded in the network.
(We will denote this number as $\widehat{K}^{\text{Scree}}$.)
We want to note the readers that the scree-plot analysis serves as a good guideline for determining the range of grids to search over.
With the estimate of the number of topics in the network in mind, we record the $\text{rank}(\widehat{L}^{\gamma,\delta})$ and $|\widehat{S}^{\gamma,\delta}|$ for each tuning parameter pair on a given grid.
We need to go through several iterations of this recording procedure to find a proper range of grid, in which we can get $\text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}}$
and $10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X|$, via adjusting the range of grid for $\gamma$ and $\delta$ repeatedly.
Once we find a grid, which satisfies above constraints, we choose a pair of tuning parameters: %($\gamma^{\text{Heu}},\delta^{\text{Heu}}$):
\[
    (\gamma^{\text{Heu}},\delta^{\text{Heu}}):=
    \big\{(\gamma,\delta): \text{rank}(\widehat{L}^{\gamma,\delta})=\widehat{K}^{\text{Scree}},
    \mbox{mode} |\widehat{S}^{\gamma,\delta}|: \mbox{subject to} 10^{-4}|X| \leq |\widehat{S}^{\gamma,\delta}| \leq 10^{-1}|X| \big\}
\]
One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) and the AIC, work where we recall that BIC and AIC are defined as follows:
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \bigg(\frac{n(n-1)}{2}\bigg),
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|.
\]
Here $M$ indicates the current model, which is implicitly understood that the model is obtained from certain tuning parameter pair $(\gamma,\delta)$.
We use $\mathbb{L}_n( \hat{\beta}(M))$ to denote the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $\widehat{S}^{\gamma,\delta}$ and the low-rank matrix $\widehat{L}^{\gamma,\delta}$.
In detail, if we have $\text{rank}(\widehat{L}^{\gamma,\delta})=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} \neq 0\}} + n K - \frac{K(K-1)}{2} + 1 ;
\]
since the number of free parameters in $\widehat{L}^{\gamma,\delta}$ is $K$ plus $nK - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
Additional $1$ in the last term is due to $\hat{\alpha}$.
We want to find a pair $(\gamma,\delta)$, which minimizes BIC($M$) and AIC($M$) as a function of $(\gamma,\delta)$ respectively, where we denote them as follows:
\[
    (\gamma^{BIC},\delta^{BIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{BIC}(M),
    \quad
    (\gamma^{AIC},\delta^{AIC}):= \mbox{arg min}_{\gamma, \delta}
    \mbox{AIC}(M)
\]
We evaluate the models that are selected via our heuristic approach, BIC, and AIC by using following four evaluation metrics.

@@

\subsubsection{Several Observations} \label{sec:obs}
%Given a network data $X$, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to $k$th topic or not.
%We apply a simple $k$-means clustering on the fitted $L$ matrix's $K$ eigenvectors.
%For the illustration of performance of our fitted model after applying $k$-means algorithm on three synthetic scenarios, in Fig\ref{fig:figure1}, we plot the coordinates of each rows of first two eigen-vectors on $2$D plane.
%Furthermore, we find one interesting phenomenon.
%Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
%Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.
\begin{enumerate}
    \item \textbf{Model Selection.}
    First and foremost, choosing a good pair of tuning parameters is critical when it comes to making a good statistical inference on data.
    As presented in Table.\ref{tab:table1}, both BIC and AIC, which are well known for their model selection consistency in asymptotic setting, appear to under-estimate either the number of topics or the number of ad-hoc links in the networks in our synthetic settings. This may be caused by the fact that these traditional methods take the sample size into account, and therefore penalizes the model complexity too harshly.
    In the heuristic approach, scree-plot plays an important role when it comes to recovering the number of topics, and this strategy leads us to good model selection results for all the six cases considered in two scenarios. (See Fig.$\ref{fig:figure2}$)

    \begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &    1 (3)  &    0 (2)   &  0 (2)  &    1 (4)    &  0 (3)   &  0 (3)  &    1 (5)  &   0 (4)    & 0 (4) \\
    $M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
    $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
    $M_{4}$   &  0  &    10/30    &  10/30     &   0   &   20/80    &   20/80   &  0      &  24/120     &   24/120    \\
                \hline
    \end{tabular}

    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 2}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 4} & \multicolumn{3}{c|}{Case 5} & \multicolumn{3}{c}{Case 6} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  &    Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &   1 (3)     &     1 (3)  &  1 (3)    &      1 (3)   &   1 (3)    &  1 (3)    &   1 (3)     &  1 (3)   & 1 (3)   \\
    $M_{2}$   &   17/18   &   0    &    0  &   17/18     &   0    &  0    &  16/18    &   0    &  0    \\
    $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
    $M_{4}$   &  0  &   0    &  0    &   0          &   0    &   0   &  0      &  0     &   0   \\
                \hline
    \end{tabular}
    \caption{ For two scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
    Also note that it chooses a model whose mis-classification rate is close to $0$.
    A number in the parentheses represents the rank of $\widehat{L}$ estimated from ($\gamma^{\text{Heu}},\delta^{\text{Heu}}$), ($\gamma^{\text{AIC}},\delta^{\text{AIC}}$) and ($\gamma^{\text{BIC}},\delta^{\text{BIC}}$) for each case.}
    \label{tab:table1}
    \end{table}
